A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-10 implementation.tex
Drop claim about minimsation
Closes: #44 (in the bluntest possible way).

Ping @pruemmer for possibly a better claim.

As an optimisation, our automata (including intermittent products) have dead
states eliminated during construction. Any automaton we produce contains only
states that are both reachable from the initial state and has a path to an
accepting state. We never perform any other minimisation on the automata for
either backend. More complex minimisation was left out since performing
minimisation on automata with counters is non-trivial, and minimising symbolic
automata risks exponential blowup~\cite{minimising-symbolic}.

>>>>

As an optimisation, our automata (including intermittent products) have dead
states eliminated during construction. Any automaton we produce contains only
states that are both reachable from the initial state and has a path to an
accepting state. We never perform any other minimisation on the automata for
either backend. More complex minimisation was left out since performing
minimisation on automata with counters is non-trivial.

% @ AS: I did the simple thing and dropped the claim about symbolic automata
% here: ours are less symbolic (i.e. typically finite) than the ones in the
% cited paper, and so are technically no worse than normal non-symbolic ones.
